---
title: "Orwell paper descriptive analysis data dump"
author: "Azzah (C4C)"
date: "`r Sys.Date()`"
output:
  pdf_document: default
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
```

```{r environment-data-setup, include = F}
##### PRELIMINARIES #####
# Clear console and environment 
graphics.off(); rm(list=ls());cat("\14");

# Load packages
#install.packages("pacman") # install the package if you haven't 
pacman::p_load(tidyverse,data.table,dplyr,knitr,tinytex,corrplot,stringr,summarytable,makecell,
               Hmisc,showtext,stats,pollster,sjPlot,psych,lavaan, viridis, texreg, kableExtra,
               rempsyc, effectsize, flextable, broom, report, stargazer, modelsummary, margins)

# Retrieve the current system username
current_user <- Sys.info()[["user"]]

# Check if the username matches and set the working directory accordingly
if (current_user == "User") {
  base_dir <- "H:/"
} else if (current_user %in% c("azzah", "USER")) {
  base_dir <- "G:/"
} 

# Set directory
master <- file.path(base_dir, 
                    "Shared drives", 
                    "Projects", 
                    "2025", 
                    "Orwell", 
                    "Breadcrumbs", 
                    "10 Quantitative Narrative Testing", 
                    "9 Main survey")
setwd(master)

arc = file.path(getwd(), "1 archive")
ipt = file.path(getwd(),"2a input")
temp = file.path(getwd(),"2b temp")
opt = file.path(getwd(),"2c output")
lg = file.path(getwd(),"3 log")
fig = file.path(getwd(),"4 figures")
tbl = file.path(getwd(),"5 tables")

##### DATA PREPARATION #####
# Set data date
date <- "20250304"

# Load data
dataname <- paste0("processed_",date,".csv") 
data <- file.path(temp,dataname) 
rdf <- fread(data)

# Generate value for total obs
total = nrow(rdf)
```


``` {r setup_plot_detail}
##### SET UP PLOT DETAILS #####
# Set graphic dimension for upcoming graphs
width = 3840
height = 2094
res = 300

# Setup custom font for plots
font_add_google("Barlow", "barlow")
showtext_auto()

# setting palette for plotplainblind
plotplainblind <- grDevices::colorRampPalette(
          colors = c("#808080", "#d0d0d0", "#abdaf4","#80cfb9","#f3cf80","#e6bcd3","#eaaf80", "#80b9d9","#f8f2a1"))(9)

subtitle <- paste0("(N=", total, ")")

# Setup template customization for plot
custom_theme <- function() {
  theme_minimal() +
    theme(
      legend.position = "bottom",
      legend.margin = margin(t = -20),
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      text = element_text(family = "barlow"),
      plot.title = element_text(face = "bold"),
      axis.text.x = element_text(angle = 0,
                                 hjust = 0.5,
                                 vjust = 5,
                                 size = 10
      )
    )
}

```

``` {r prep_variables}

cb_data <- rdf %>%
  select(record, lfCB, starts_with("CB"), crt_intrpt_msg, agreestim)

# generate dummy for agreeing with statement
cb_data <- cb_data %>%
  mutate(
    d_agree = factor(agreestim,
                     levels=c(0,1),
                     labels=c("Disagree", "Agree")))

## notes: g agreestim=(lfCB==6)|(inrange(CB04,4,6) & (inrange(lfCB,1,3) | lfCB==5))|(inrange(CB04,1,3) & lfCB==4)


# generate dummy for correct interpretation
narrative <- c("A", "B", "C", "D", "E")

for (x in narrative) {
  col_name <- paste0("CB01_cor_", x)
  cb01_col <- paste0("CB01", x)

  if (x == "D") {
    cb_data <- cb_data %>%
      mutate(!!sym(col_name) := ifelse(CB01D >= 2 & CB01D <= 3, 1, 0))
  } else {
    cb_data <- cb_data %>%
      mutate(!!sym(col_name) := ifelse(!!sym(cb01_col) == 1, 1, 0))
  }
  
cb_data <- cb_data %>%
    mutate(!!sym(col_name) := ifelse(lfCB == 6, 1, !!sym(col_name)))
}



correct_cols <- paste0("CB01_cor_", narrative)

cb_data <- cb_data %>%
  rowwise() %>%
  mutate(d_correct := max(c_across(all_of(correct_cols)), na.rm = TRUE)) %>%
  ungroup()

cb_data$d_correct <- factor(cb_data$d_correct, 
                             levels = c(0, 1), 
                             labels = c("Incorrect", "Correct"))
```


``` {r demog_prep}
## prepare demographics
demographics <- rdf %>%
  mutate(prov = ID01) %>%
  mutate(urban = case_when(
    ID02 == 1 ~ 1,
    ID02 == 2 ~ 0
  )) %>%
  mutate(urban = factor(urban,
                        levels = c(1,0),
                        labels = c("Urban", "Rural"))) %>%
  mutate(gender = case_when(
    ID03 == 1 ~ 1,
    ID03 == 2 ~ 0
  )) %>%
  mutate(gender = factor(male,
                       levels = c(1,0),
                       labels = c("Male", "Female"))) %>%
  mutate(age = ID04) %>%
  mutate(age_group = case_when(
    age>=18 & age<=24 ~ 1,
    age>=25 & age<=34 ~ 2,
    age>=35 & age<=44 ~ 3, 
    age>=45 & age<=54 ~ 4,
    age>=55 & age<=64 ~ 5
  )) %>%
  mutate(age_group=factor(age_group,
                          levels = c(1,2,3,4,5),
                          labels = c("18-24", "25-34", "35-44", "45-54", "55-64"))) %>%
	mutate(educ = factor(ID06,
	                     levels = c(1,2,3,4,5),
	                     labels = c("Below primary school", "Primary school", 
	                                "Junior high school", "High school", "Higher education")))

demographics <- demographics %>%
  select(record, prov, urban, age, age_group, male, educ)


```


## 1) Tabulation: % of accuracy and % agreement of those who is correctly interpret
``` {r sum_accurate}
# Calculate percentage of correct interpretation by narrative
sum_accurate <- cb_data %>%
  group_by(lfCB, d_correct) %>%
  summarise(freq = n(), .groups = "drop") %>%
  group_by(lfCB) %>%
  mutate(total_nar = sum(freq), .groups = "drop") %>%
  group_by(lfCB, d_correct) %>%
  mutate(percent_correct = (freq/total_nar)*100)

sum_accurate_kable <- sum_accurate %>%
  filter(d_correct == "Correct") %>%
  rename(stimulus = lfCB) %>%
  select(stimulus, percent_correct)


# Calculate percentage of agree by narrative and accuracy
sum_agree <- cb_data %>%
  group_by(lfCB, d_correct, d_agree) %>%
  summarise(freq = n(), .groups = "drop") %>%
  group_by(lfCB, d_correct) %>%
  mutate(total_cor_nar = sum(freq), .groups = "drop") %>%
  group_by(lfCB, d_correct, d_agree) %>%
  mutate(percent_agree = (freq/total_cor_nar)*100)

sum_agree_kable <- sum_agree %>%
  filter(d_correct == "Correct" & d_agree == "Agree") %>%
  rename(stimulus = lfCB) %>%
  select(stimulus, percent_agree)

# Combining the table for specified column
sum_kable <- sum_accurate_kable %>%
  full_join(sum_agree_kable, by = "stimulus") %>%
  select(stimulus, percent_correct, percent_agree) %>%
  filter(stimulus!=6)

kable(sum_kable,
      digits = 2,
      caption = "Percentage of stimulus accuracy and agreement",
      col.names = c("Stimulus", "Correct (%)", "Agree(%)"),
      align = c("l", "r", "r")
      ) 
cat("Notes: percentage of agreement is calculated of those who interpret stimulus correctly.\n")

```

## 2) Logit regression of demographics on accuracy 
Depedent variable is binary variable of accuracy (1: correct interpretaion of stimulus, 0: incorrect interpretation). Base group for age_group is "18-24", base group for education is "Primary school"

``` {r prep_reg_data}
reg_data <- cb_data %>%
  inner_join(demographics, by = "record")
```

``` {r loop_logit_correct}

all_results <- list()

for (i in 1:5) {
  # Filter for one narrative
  data_nar <- reg_data %>%
    filter(lfCB == i) %>%
    droplevels()  # Drop unused factor levels
  
  # Run logistic regression
  model <- glm(d_correct ~ male + age_group + educ + urban,
               data = data_nar, family = "binomial")
  
  # Get marginal effects
  marginal <- margins(model)
  summary_marginal <- summary(marginal)
  
  # Format result
  formatted <- summary_marginal %>%
    as_tibble() %>%
    mutate(
      marginal_effect = scales::percent(AME, accuracy = 0.1),
      p_value = ifelse(p < 0.001, "<0.001", format(round(p, 3), nsmall = 3)),
      significance = case_when(
        p < 0.001 ~ "***",
        p < 0.01 ~ "**",
        p < 0.05 ~ "*",
        p < 0.1 ~ ".",
        TRUE ~ ""
      ),
      narrative = i
    ) %>%
    select(narrative, factor, AME, p_value, significance)
  
  all_results[[i]] <- formatted
}

# Combine all into one table
final_table <- bind_rows(all_results)


```

```{r kable_output_ame_correct, results='asis'}
# Format cell content as simple plain-text strings
formatted_table <- final_table %>%
  mutate(
    p_value_num = as.numeric(p_value),
    p_value_fmt = ifelse(
      is.na(p_value_num),
      as.character(p_value),
      sprintf("%.3f", p_value_num)
    ),
    cell = paste0(sprintf("%.3f", AME), " ", "(p = ", p_value_fmt, ")", significance)
  ) %>%
  select(narrative, factor, cell) %>%
  pivot_wider(names_from = narrative, values_from = cell, names_prefix = "Narrative ")

# Output simple PDF-friendly kable
formatted_table %>%
  rename(`Predictor` = factor) %>%
  kable(
    booktabs = TRUE,
    longtable = TRUE,
    escape = TRUE,
    caption = "Average Marginal Effects on Correct Interpretation"
  ) %>%
  kable_styling(
    latex_options = c("hold_position", "repeat_header"),
    font_size = 6.5
  ) %>%
  column_spec(1, bold = TRUE)
```



## 3) Logit regression of demographics on agreement 
Depedent variable is binary variable of agreement (1: agree with stimulus, 0: disagree). Base group for age_group is "18-24", base group for education is "Primary school"

``` {r loop_logit_agree}

all_results <- list()

for (i in 1:5) {
  # Filter for one narrative
  data_nar <- reg_data %>%
    filter(lfCB == i) %>%
    droplevels()  # Drop unused factor levels
  
  # Run logistic regression
  model <- glm(d_agree ~ male + age_group + educ + urban,
               data = data_nar, family = "binomial")
  
  # Get marginal effects
  marginal <- margins(model)
  summary_marginal <- summary(marginal)
  
  # Format result
  formatted <- summary_marginal %>%
    as_tibble() %>%
    mutate(
      marginal_effect = scales::percent(AME, accuracy = 0.1),
      p_value = ifelse(p < 0.001, "<0.001", format(round(p, 3), nsmall = 3)),
      significance = case_when(
        p < 0.001 ~ "***",
        p < 0.01 ~ "**",
        p < 0.05 ~ "*",
        p < 0.1 ~ ".",
        TRUE ~ ""
      ),
      narrative = i
    ) %>%
    select(narrative, factor, AME, p_value, significance)
  
  all_results[[i]] <- formatted
}

# Combine all into one table
final_table <- bind_rows(all_results)


```

``` {r kable_output_ame_agree}

# Format cell content as simple plain-text strings
formatted_table <- final_table %>%
  mutate(
    p_value_num = as.numeric(p_value),
    p_value_fmt = ifelse(
      is.na(p_value_num),
      as.character(p_value),
      sprintf("%.3f", p_value_num)
    ),
    cell = paste0(sprintf("%.3f", AME), " ", "(p = ", p_value_fmt, ")", significance)
  ) %>%
  select(narrative, factor, cell) %>%
  pivot_wider(names_from = narrative, values_from = cell, names_prefix = "Narrative ")

# Output simple PDF-friendly kable
formatted_table %>%
  rename(`Predictor` = factor) %>%
  kable(
    booktabs = TRUE,
    longtable = TRUE,
    escape = TRUE,
    caption = "Average Marginal Effects on Agreement to Stimulus"
  ) %>%
  kable_styling(
    latex_options = c("hold_position", "repeat_header"),
    font_size = 6.5
  ) %>%
  column_spec(1, bold = TRUE)

```


\newpage
## 4) Heatmap of most evoked emotion by each statement
``` {r emotion_prep}
cb02_data <- cb_data %>%
  select(record, lfCB, starts_with("CB02"))

emotion_var <- cb02_data %>% select(starts_with("CB02")) %>% names()
cb02_base <- c("CB02Ar", "CB02Br", "CB02Cr", "CB02Dr", "CB02Er")

# Replace answer 2 "no" into 0
cb02_data <- cb02_data %>%
  mutate(across(all_of(emotion_var), ~ replace(., . %in% c(2), 0)))


# Prepare emotion name
emotion_list <- c(
  "1" = "Anger",
  "2" = "Anxiety",
  "3" = "Disgust",
  "4" = "Fear",
  "5" = "Sad",
  "6" = "Happy",
  "7" = "Calm",
  "8" = "Longing",
  "9" = "Hopeless"
)


# for narrative 1
nar1_summary_list <- list()

  for (i in 1:9) {
  emotions <- emotion_list[i] 
  emotion_col <- paste0("CB02Ar", i)

  summary_df <- cb02_data %>%
  filter(lfCB == 1) %>%
  group_by(!!sym(emotion_col)) %>%
  summarise(freq=n(), .groups = 'drop') %>%
  mutate(percent = (freq/sum(freq))*100, .groups = 'drop') %>%
  filter(!!sym(emotion_col) == 1) %>%
  mutate(emotion = emotions) %>%
  select(emotion, freq, percent) 

  nar1_summary_list[[i]] <- summary_df
  }

sum_emotion_nar1 <- bind_rows(nar1_summary_list) %>%
  mutate(narrative = 1)


# for narrative 2
nar2_summary_list <- list()

  for (i in 1:9) {
  emotions <- emotion_list[i] 
  emotion_col <- paste0("CB02Br", i)

  summary_df <- cb02_data %>%
  filter(lfCB == 2) %>%
  group_by(!!sym(emotion_col)) %>%
  summarise(freq=n(), .groups = 'drop') %>%
  mutate(percent = (freq/sum(freq))*100, .groups = 'drop') %>%
  filter(!!sym(emotion_col) == 1) %>%
  mutate(emotion = emotions) %>%
  select(emotion, freq, percent) 

  nar2_summary_list[[i]] <- summary_df
  }

sum_emotion_nar2 <- bind_rows(nar2_summary_list) %>%
  mutate(narrative = 2)


# for narrative 3
nar3_summary_list <- list()

  for (i in 1:9) {
  emotions <- emotion_list[i] 
  emotion_col <- paste0("CB02Cr", i)

  summary_df <- cb02_data %>%
  filter(lfCB == 3) %>%
  group_by(!!sym(emotion_col)) %>%
  summarise(freq=n(), .groups = 'drop') %>%
  mutate(percent = (freq/sum(freq))*100, .groups = 'drop') %>%
  filter(!!sym(emotion_col) == 1) %>%
  mutate(emotion = emotions) %>%
  select(emotion, freq, percent) 

  nar3_summary_list[[i]] <- summary_df
  }

sum_emotion_nar3 <- bind_rows(nar3_summary_list) %>%
  mutate(narrative = 3)


# for narrative 4
nar4_summary_list <- list()

  for (i in 1:9) {
  emotions <- emotion_list[i] 
  emotion_col <- paste0("CB02Dr", i)

  summary_df <- cb02_data %>%
  filter(lfCB == 4) %>%
  group_by(!!sym(emotion_col)) %>%
  summarise(freq=n(), .groups = 'drop') %>%
  mutate(percent = (freq/sum(freq))*100, .groups = 'drop') %>%
  filter(!!sym(emotion_col) == 1) %>%
  mutate(emotion = emotions) %>%
  select(emotion, freq, percent) 

  nar4_summary_list[[i]] <- summary_df
  }

sum_emotion_nar4 <- bind_rows(nar4_summary_list) %>%
  mutate(narrative = 4)


# for narrative 5
nar5_summary_list <- list()

  for (i in 1:9) {
  emotions <- emotion_list[i] 
  emotion_col <- paste0("CB02Er", i)

  summary_df <- cb02_data %>%
  filter(lfCB == 5) %>%
  group_by(!!sym(emotion_col)) %>%
  summarise(freq=n(), .groups = 'drop') %>%
  mutate(percent = (freq/sum(freq))*100, .groups = 'drop') %>%
  filter(!!sym(emotion_col) == 1) %>%
  mutate(emotion = emotions) %>%
  select(emotion, freq, percent) 

  nar5_summary_list[[i]] <- summary_df
  }

sum_emotion_nar5 <- bind_rows(nar5_summary_list) %>%
  mutate(narrative = 5)


## Binding all narratives' emotion

sum_emotion_all <- bind_rows(sum_emotion_nar1, sum_emotion_nar2, sum_emotion_nar3,
                             sum_emotion_nar4, sum_emotion_nar5)


```

``` {r heatmap+_emotion}

breaks_val <- c(0, 20, 40, 60, 80)
colors_val <- c("white", "#D3D3D3", "#808080", "#595959", "#363636") # Example gray scale

obs_counts <- cb02_data %>%
  group_by(narrative = factor(ifelse(lfCB == 1, 1,
                                     ifelse(lfCB == 2, 2,
                                            ifelse(lfCB == 3, 3,
                                                   ifelse(lfCB == 4, 4, 
                                                          ifelse(lfCB == 5,5,NA))))))) %>%
  summarise(n_obs = n(), .groups = 'drop')

label_nar <- paste0(levels(factor(sum_emotion_all$narrative)),
                    "\n(n=", obs_counts$n_obs, ")")

heatmap_emo <- ggplot(sum_emotion_all, aes(x = factor(narrative), y = reorder(emotion, (percent)), fill = percent)) +
  geom_tile() +
  scale_fill_gradientn(colors = colors_val, breaks = breaks_val, limits = c(0, 80)) +
  geom_text(aes(label = round(percent, 2)), color = "black", size = 3) +
  #facet_wrap(~ Foundation, scales = "free") +
  labs(title = "Emotions evoked by each narrative (%)",
       #subtitle = subtitle,
       x = "Narrative",
       y = "Emotion",
       fill = "Percentage") +
  theme_minimal() +
  custom_theme() +
  scale_x_discrete(position="top",
                   labels = label_nar) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5, hjust=0.5),
        legend.position = "right")
print(heatmap_emo)
```


## 4a) Test of two proportion for evoked emotion and agreement
``` {r proportion_emotion}

cb02_data_all <- cb_data %>%
  select(record, d_correct, d_agree) %>%
  inner_join(cb02_data, by = "record")


results_df <- data.frame()

for (nar in 1:5) {
  for (i in 1:9) {
    emotion_col <- paste0("CB02", LETTERS[nar], "r", i)
    emotion_name <- emotion_list[as.character(i)]

    temp_table <- cb02_data_all %>%
      filter(lfCB == nar) %>%
      mutate(selected = !!sym(emotion_col) == 1) %>%
      group_by(d_agree, selected) %>%
      summarise(count = n(), .groups = "drop") %>%
      pivot_wider(names_from = selected, values_from = count, values_fill = 0)

    if (nrow(temp_table) == 2 && all(c("TRUE", "FALSE") %in% colnames(temp_table))) {
      x <- c(temp_table$`TRUE`[1], temp_table$`TRUE`[2])
      n <- rowSums(temp_table[, c("TRUE", "FALSE")])
      test <- prop.test(x = x, n = n)
      
      sig_star <- case_when(
        test$p.value <= 0.001 ~ "***",
        test$p.value <= 0.01  ~ "**",
        test$p.value <= 0.05  ~ "*",
        TRUE                  ~ ""
        )

      results_df <- rbind(results_df, data.frame(
        narrative = nar,
        emotion = emotion_name,
        agree_yes = x[2],
        agree_total = n[2],
        disagree_yes = x[1],
        disagree_total = n[1],
        p_value = round(test$p.value, 4),
        agree_prop = round(test$estimate[2], 3),
        disagree_prop = round(test$estimate[1], 3),
        significance = sig_star
      ))
    }
  }
}

```

``` {r kable_proportion_test}

narrative_tables <- results_df %>%
  arrange(narrative, emotion) %>%
  group_split(narrative)

kable_outputs <- list() # Create an empty list to store the kable outputs

for (i in 1:5) {
  caption_kable <- paste0("Emotion differences of agree and disagree groups \n(Narrative ", i, ")")
  kable_name <- paste0("kable_", i)
  
  table_data <- narrative_tables[[i]] %>%
    mutate(
      agree_prop = scales::percent(agree_prop, accuracy = 1),
      disagree_prop = scales::percent(disagree_prop, accuracy = 1),
      p_value = ifelse(p_value < 0.001, "<0.001", sprintf("%.3f", p_value))
    ) %>%
    select(emotion, agree_prop, disagree_prop, p_value, significance)

  kable_outputs[[i]] <- kable(
    table_data,
    caption = caption_kable,
    col.names = c("Emotion", "Agree (%)", "Disagree (%)", "P-value", "Sig"),
    align = c("l", "r", "r", "r", "c")
  ) %>%
    kable_styling(font_size = 10, full_width = FALSE) %>%
    column_spec(1, width = "8em") %>%
    column_spec(2:4, width = "6em") %>%
    column_spec(5, width = "3em")
}
```

``` {r print_kable, , results='asis'}
print(kable_outputs[1])
cat("\\newpage\n")

for (i in 2:4) {
  print(kable_outputs[[i]])
  cat("\n") # Add a newline for spacing
}

cat("\\newpage\n")
print(kable_outputs[5])
```


\newpage
## 5) Bar chart of sentence resonance

### Narrative 1 - Sentence resonance by correct interpretation
``` {r prep_cb03a_correct}

sum_cb03_correct_nar1 <- cb_data %>%
  filter(lfCB == 1) %>%
  group_by(d_correct, CB03A) %>%
  summarise(freq = n(), .groups='drop') %>%
  group_by(d_correct) %>%
  mutate(total_correct = sum(freq), .groups = 'drop') %>%
  mutate(percent = (freq/total_correct)*100) %>%
  mutate(sentence = factor(CB03A,
                           levels = c(1,2,3,4),
                           labels = c("What is the point of Indonesia continuing to develop\nif only a few people get to experience the results?",
                                      "All this time, the benefits of development have not\nreached all citizens.Those who enjoy it are the rich and\npowerful.Those at the bottom are still not prosperous.",
                                      "The government should improve the distribution of\ndevelopment benefits.The government must ensure that\nthe benefits can be enjoyed by all Indonesians.",
                                      "If the government can improve the distribution of\ndevelopment benefits,then all levels of society can thrive\nand improve their standard of living wherever they are.")))



```

``` {r plot_cb03a_correct, fig.width = 10, fig.height = 3.5}

label_counts <- sum_cb03_correct_nar1 %>%
  filter(CB03A==1) %>%
  select(d_correct, total_correct) %>%
  mutate(label = paste0(d_correct, " (n = ", total_correct, ")")) %>%
  select(d_correct, label) %>%
  deframe()  # Convert to named vector


# Bar plot
p_cb03_nar1 <- ggplot(sum_cb03_correct_nar1) +
    aes(x = sentence, y = percent) +
    facet_wrap(~d_correct, nrow=1, strip.position="top",
               labeller = labeller(d_correct = label_counts)) +
    geom_bar(stat = "identity", fill=plotplainblind[1]) +
    geom_text(aes(label = paste(round(percent, 0),"%")),
      vjust = 0.5,
      hjust = -0.1,
      size = 4
    ) +
    coord_flip() +
  scale_y_continuous(limit = c(0,50), labels=NULL) +
    labs(
      #title = paste("Sentence resonance of narrative 1"),
      #subtitle = subtitle,
      x = "",
      y = ""
    ) +
  custom_theme() +
  theme(
    legend.position = "none",
    plot.caption = element_text(hjust=0),
    strip.text = element_text(size = 11)
  ) 
print(p_cb03_nar1)

```

### Narrative 1 - Sentence resonance by agreement
``` {r prep_cb03a_agree}

sum_cb03_nar1 <- cb_data %>%
  filter(lfCB == 1) %>%
  group_by(d_agree, CB03A) %>%
  summarise(freq = n(), .groups='drop') %>%
  group_by(d_agree) %>%
  mutate(total_agree = sum(freq), .groups = 'drop') %>%
  mutate(percent = (freq/total_agree)*100) %>%
  mutate(sentence = factor(CB03A,
                           levels = c(1,2,3,4),
                           labels = c("What is the point of Indonesia continuing to develop\nif only a few people get to experience the results?",
                                      "All this time, the benefits of development have not\nreached all citizens.Those who enjoy it are the rich and\npowerful.Those at the bottom are still not prosperous.",
                                      "The government should improve the distribution of\ndevelopment benefits.The government must ensure that\nthe benefits can be enjoyed by all Indonesians.",
                                      "If the government can improve the distribution of\ndevelopment benefits,then all levels of society can thrive\nand improve their standard of living wherever they are.")))



```

``` {r plot_cb03a_agree, fig.width = 10, fig.height = 3.5}

label_counts <- sum_cb03_nar1 %>%
  filter(CB03A==1) %>%
  select(d_agree, total_agree) %>%
  mutate(label = paste0(d_agree, " (n = ", total_agree, ")")) %>%
  select(d_agree, label) %>%
  deframe()  # Convert to named vector

# Bar plot
p_cb03_nar1 <- ggplot(sum_cb03_nar1) +
    aes(x = sentence, y = percent) +
    facet_wrap(~d_agree, nrow=1, strip.position="top",
               labeller = labeller(d_agree = label_counts)) +
    geom_bar(stat = "identity", fill=plotplainblind[1]) +
    geom_text(aes(label = paste(round(percent, 0),"%")),
      vjust = 0.5,
      hjust = -0.1,
      size = 4
    ) +
    coord_flip() +
  scale_y_continuous(limit = c(0,50), labels=NULL) +
    labs(
      #title = paste("Sentence resonance of narrative 1"),
      #subtitle = subtitle,
      x = "",
      y = ""
    ) +
  custom_theme() +
  theme(
    legend.position = "none",
    plot.caption = element_text(hjust=0),
    strip.text = element_text(size = 11)
  ) 
print(p_cb03_nar1)

```

### Narrative 2 - Sentence resonance by correct interpretation
### Narrative 2 - Sentence resonance by agreement

### Narrative 3 - Sentence resonance by correct interpretation
### Narrative 3 - Sentence resonance by agreement

### Narrative 4 - Sentence resonance by correct interpretation
### Narrative 4 - Sentence resonance by agreement

### Narrative 5 - Sentence resonance by correct interpretation
### Narrative 5 - Sentence resonance by agreement


\newpage
## 6) Demographics figure (Statistical difference of key characteristics between the sample and the population) -- see paper draft [upcoming]